An Example Article\tfootnote{This is a title footnote}

### 2024-01-09 amsart-en/amsart-temp.tex
update

% package for bibliography support
\usepackage[numbers,sort&compress]{natbib}

@@

\begin{abstract}
  This is an example \LaTeX\ article. This can be used as a
  template for new articles.  Abstracts must be able to stand alone
  and so cannot contain citations to the paper's references,
  equations, etc.  An abstract must consist of a single paragraph and
  be concise. Because of online formatting, abstracts must appear as
  plain as possible. Any equations should be inline.
\end{abstract}

@@

\section{Introduction}
The introduction introduces the context and summarizes the manuscript.
It is important to clearly state the contributions of this piece of work.

@@

This is a citation example \cite{Adams2003}. This statement requires
citation \cite{Shen1994,Tadmor2012,TreWei2014}.

@@

\section*{Acknowledgments}
We would like to acknowledge the assistance of volunteers in putting
together this example manuscript and supplement.

>>>>

% package for bibliography support
\usepackage{cite}
%\usepackage[numbers,sort&compress]{natbib}

@@

\begin{abstract}
This is an example \LaTeX\ article. This can be used as a template for new articles.
Abstracts must be able to stand alone and so cannot contain citations to the paper's references,equations, etc.
An abstract must consist of a single paragraph and be concise.
Because of online formatting, abstracts must appear as plain as possible.
Any equations should be inline.
\end{abstract}

@@

\section{Introduction}

The introduction introduces the context and summarizes the manuscript.
It is important to clearly state the contributions of this piece of work.

@@

This is a citation example \cite{Adams2003,TreWei2014}.
This statement requires citations \cite{Shen1994,Tadmor2012,TreWei2014}.

@@

\section*{Acknowledgments}

We would like to acknowledge the assistance of volunteers in putting together this example manuscript and supplement.

### 2024-01-09 amsart-en/amsart-temp2.tex
update

% package for bibliography support
\usepackage[numbers,sort&compress]{natbib}

@@

\author[Author A]{Author A$^{1}$}
\author[Author B]{Author B$^{2}$}
\author[Author C]{Author C$^{1,*}$}
\address{$^{1}$Common address of authors A and B}
\address{$^{2}$author C address}

%\author[Author A, Author B]{Author A$^{1}$, Author B$^{1,*}$}
%\address{$^{1}$common address of authors A and B}
%\author[Author C]{Author C$^{2}$}
%\address{$^{2}$author C address}

@@

\begin{theorem}[Mean Value Theorem]\label{thm:mvt}
  Suppose $f$ is a function that is continuous on the closed interval
  $[a,b]$.  and differentiable on the open interval $(a,b)$.
  Then there exists a number $c$ such that $a < c < b$ and
  \begin{equation*}
    f'(c) = \frac{f(b)-f(a)}{b-a}.
  \end{equation*}
  In other words,
  \begin{equation*}
    f(b)-f(a) = f'(c)(b-a).
  \end{equation*}
\end{theorem}

@@

Some description and explanation of pictures and tables

>>>>

% hyperlink setting
%\hypersetup{
%  colorlinks=true,
%  linkcolor=magenta,
%  citecolor=blue,
%  filecolor=blue,
%  urlcolor=blue
%}

% package for bibliography support
\usepackage{cite}
%\usepackage[numbers,sort&compress]{natbib}

@@

\author[Author A]{Author A$^{1}$}
\author[Author B]{Author B$^{2}$}
\author[Author C]{Author C$^{1,*}$}
\address{$^{1}$Common address of authors A and B}
\address{$^{2}$Author C address}

%\author[Author A, Author B]{Author A$^{1}$, Author B$^{1,*}$}
%\address{$^{1}$Common address of authors A and B}
%\author[Author C]{Author C$^{2}$}
%\address{$^{2}$Author C address}

@@

\begin{theorem}[Mean Value Theorem]\label{thm:mvt}
  Suppose $f$ is a function that is continuous on the closed interval $[a,b]$ and differentiable on the open interval $(a,b)$.
  Then there exists a number $c$ such that $a < c < b$ and
  \begin{equation*}
    f'(c) = \frac{f(b)-f(a)}{b-a}.
  \end{equation*}
  In other words,
  \begin{equation*}
    f(b)-f(a) = f'(c)(b-a).
  \end{equation*}
\end{theorem}

@@

Some description and explanation of pictures and tables.

### 2024-01-09 article-en/article-temp-info.tex
update

% package for mathematics
\usepackage{amsmath,amssymb,amsthm}
% package for RSFS fonts in maths
\usepackage{mathrsfs}
% package for special symbols
\usepackage{pifont}
% package for multilingual support
\usepackage[english]{babel}
% package for figures
\usepackage{graphicx}
\usepackage{subfigure}
% package for hyperlink
\usepackage{hyperref}
% package for layout of list
\usepackage{enumitem}
% package for showing keys in draft mode
\usepackage[notcite,notref]{showkeys}
% package for color
\usepackage{color}
% package for table
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{makecell}
% package for multiple columns and rows
\usepackage{multirow,multicol}
% package for caption
\usepackage{caption}
% package for algorithm
\usepackage{algorithm,algorithmicx}
\usepackage{algpseudocode}
% package for author and affiliation style
\usepackage[affil-it]{authblk}
% package for using box and verbatim
\usepackage{fancybox}
% package for page headers and footers
\usepackage{fancyhdr}

@@

\newcommand\cormark{\raisebox{-1.6pt}{*}}
\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  %\addtocounter{footnote}{-1}%
  \endgroup
}

@@

% Information for title and author
\title{An Example Article}

@@

\begin{abstract}
  This is an example \LaTeX\ article. This can be used as a
  template for new articles.  Abstracts must be able to stand alone
  and so cannot contain citations to the paper's references,
  equations, etc.  An abstract must consist of a single paragraph and
  be concise. Because of online formatting, abstracts must appear as
  plain as possible. Any equations should be inline.

  \medskip
  \noindent{\bf Keywords}: Example, \LaTeX, numerical methods

  \medskip
  \noindent{\bf 2000 Mathematics Subject Classification: } 65L60, 65L05, 65L70.
\end{abstract}

\section{Introduction}
The introduction introduces the context and summarizes the
manuscript. It is importantly to clearly state the contributions of
this piece of work.

@@

Display matrices can be rendered using environments from \texttt{amsmath}:
\begin{equation}\label{eq:matrices}
S=\begin{bmatrix}1&0\\0&0\end{bmatrix}
\quad\text{and}\quad
C=\begin{pmatrix}1&1&0\\1&1&0\\0&0&0\end{pmatrix}.
\end{equation}
Equation \ref{eq:matrices} shows some example matrices.

@@

\begin{table}[htp!]
\centering
\newcolumntype{L}{X}
\newcolumntype{C}{>{\centering \arraybackslash}X}
\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
\renewcommand\arraystretch{1.2}
\caption{Table description}
\label{tab:error}
\begin{tabularx}{0.8\textwidth}{|P{0.8cm}|C|C|C|C|C|}
\Xhline{2\arrayrulewidth}
N  & A       & B    & C       & D      & E     \\
\Xhline{2\arrayrulewidth}
2  & 9.20E-05 & 9.90E-05 & 1.00E-06 & 8.00E-06 & 1.50E-05 \\
4  & 9.80E-05 & 8.00E-05 & 7.00E-06 & 1.40E-05 & 1.60E-05 \\
6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
%14 & 2.30E-05 & 5.00E-06 & 8.20E-05 & 8.90E-05 & 9.10E-05 \\
%16 & 7.90E-05 & 6.00E-06 & 1.30E-05 & 9.50E-05 & 9.70E-05 \\
\Xhline{2\arrayrulewidth}
\end{tabularx}
\end{table}

Use \texttt{minipage} package to set images side-by-side, each with its own title, as shown in Figure~\ref{fig:A} and Figure~\ref{fig:B}.
\begin{figure}[htp!]
\begin{minipage}[t]{0.48\linewidth}
  \centering
  \includegraphics[width=0.96\linewidth]{fig1}
  \caption{Caption A}
  \label{fig:A}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\linewidth}
\centering
   \includegraphics[width=0.96\linewidth]{fig2}
   \caption{Caption B}
   \label{fig:B}
\end{minipage}
\end{figure}

@@

\section*{Acknowledgments}
We would like to acknowledge the assistance of volunteers in putting
together this example manuscript and supplement.

% References
\bibliographystyle{plain}
%\bibliographystyle{abbrv}

>>>>

% package for mathematics
\usepackage{amsmath,amssymb,amsthm}
% package for RSFS fonts in maths
\usepackage{mathrsfs}
% package for special symbols
\usepackage{pifont}
% package for multilingual support
\usepackage[english]{babel}
% package for figures
\usepackage{graphicx}
\usepackage{subfig}
% package for hyperlink
\usepackage{hyperref}
% package for layout of list
\usepackage{enumitem}
% package for showing keys in draft mode
\usepackage[notcite,notref]{showkeys}
% package for color
\usepackage{color}
% package for table
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{makecell}
% package for multiple columns and rows
\usepackage{multirow,multicol}
% package for caption
\usepackage{caption}
% package for algorithm
\usepackage{algorithm,algorithmicx}
\usepackage{algpseudocode}
% package for author and affiliation style
\usepackage[affil-it]{authblk}
% package for using box and verbatim
\usepackage{fancybox}
% package for page headers and footers
\usepackage{fancyhdr}

@@

\newcommand\cormark{\raisebox{-1.6pt}{*}}
\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  %\addtocounter{footnote}{-1}%
  \endgroup
}
\newcommand{\tfootnote}[1]{%
  \textsuperscript{$\star$}%
  {\renewcommand{\thefootnote}{$\star$}%
  \footnotetext{#1}}
}

@@

% Information for title and author
\title{An Example Article\tfootnote{This is a title footnote}}

@@

\begin{abstract}
This is an example \LaTeX\ article. This can be used as a template for new articles.
Abstracts must be able to stand alone and so cannot contain citations to the paper's references,equations, etc.
An abstract must consist of a single paragraph and be concise.
Because of online formatting, abstracts must appear as plain as possible.
Any equations should be inline.

\medskip
\noindent{\bfseries Keywords}: Example, \LaTeX, numerical methods

\medskip
\noindent{\bfseries Mathematics Subject Classification:} 65M60, 65M12.
\end{abstract}

\section{Introduction}

The introduction introduces the context and summarizes the manuscript.
It is important to clearly state the contributions of this piece of work.

@@

Display matrices can be rendered using environments from \texttt{amsmath}:
\begin{equation}\label{eq:matrices}
S=\begin{bmatrix}
1 & 0 \\
0 & 0
\end{bmatrix}
\quad\text{and}\quad
C=\begin{pmatrix}
1 & 1 & 0 \\
1 & 1 & 0 \\
0 & 0 & 0
\end{pmatrix}.
\end{equation}
Equation \ref{eq:matrices} shows some example matrices.

@@

\begin{table}[htp!]
\centering
\newcolumntype{L}{X}
\newcolumntype{C}{>{\centering \arraybackslash}X}
\newcolumntype{R}{>{\raggedleft \arraybackslash}X}
\newcolumntype{P}[1]{>{\centering \arraybackslash}p{#1}}
\renewcommand\arraystretch{1.2}
\caption{Table description}
\label{tab:error}
\begin{tabularx}{0.8\textwidth}{|P{0.8cm}|C|C|C|C|C|}
\Xhline{2\arrayrulewidth}
$N$  & A       & B    & C       & D      & E     \\
\Xhline{2\arrayrulewidth}
2  & 9.20E-05 & 9.90E-05 & 1.00E-06 & 8.00E-06 & 1.50E-05 \\
4  & 9.80E-05 & 8.00E-05 & 7.00E-06 & 1.40E-05 & 1.60E-05 \\
6  & 4.00E-06 & 8.10E-05 & 8.80E-05 & 2.00E-05 & 2.20E-05 \\
8  & 8.50E-05 & 8.70E-05 & 1.90E-05 & 2.10E-05 & 3.00E-06 \\
10 & 8.60E-05 & 9.30E-05 & 2.50E-05 & 2.00E-06 & 9.00E-06 \\
12 & 1.70E-05 & 2.40E-05 & 7.60E-05 & 8.30E-05 & 9.00E-05 \\
%14 & 2.30E-05 & 5.00E-06 & 8.20E-05 & 8.90E-05 & 9.10E-05 \\
%16 & 7.90E-05 & 6.00E-06 & 1.30E-05 & 9.50E-05 & 9.70E-05 \\
\Xhline{2\arrayrulewidth}
\end{tabularx}
\end{table}

Use \texttt{minipage} package to set images side-by-side, each with its own title, as shown in Figure~\ref{fig:A} and Figure~\ref{fig:B}.

\begin{figure}[htp!]
\begin{minipage}[t]{0.48\linewidth}
  \centering
  \includegraphics[width=0.96\linewidth]{fig1}
  \caption{Caption A}
  \label{fig:A}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\linewidth}
\centering
   \includegraphics[width=0.96\linewidth]{fig2}
   \caption{Caption B}
   \label{fig:B}
\end{minipage}
\end{figure}

Use \texttt{subfig} package to set subfigure, each with its subcaption, as shown in Figure~\ref{fig:twosubfig}.

\begin{figure}[htp!]
\centering
\subfloat[Subcaption A]{\includegraphics[width=0.46\linewidth]{fig1}}
\qquad
\subfloat[Subcaption B]{\includegraphics[width=0.46\linewidth]{fig2}}
\caption{Two subfigures}
\label{fig:twosubfig}
\end{figure}

@@

\section*{Acknowledgments}

We would like to acknowledge the assistance of volunteers in putting together this example manuscript and supplement.

% References
%\bibliographystyle{plain}
\bibliographystyle{abbrv}
